Social Feedback For Robotic Collaboration

### 2016-05-16 paper.tex
adjusting for rss stylesheet

\documentclass{article}

\usepackage{multicol}

\usepackage{float}

\usepackage[margin=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{natbib}
\usepackage{bbm}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{calc,positioning,shapes,arrows}
%\usepackage{natbib}
%\bibliographystyle{unsrtnat}
\newcommand{\Iota}{\mathcal{I}}

\bibliographystyle{unsrtnat}
\setlength{\columnsep}{0.8cm}

\title{Social Feedback For Robotic Collaboration}
\author{Emily Wu}

\begin{document}
\pagenumbering{gobble}

\vspace*{8cm}

\begin{raggedleft}
	\scshape
	\huge \textbf{Social Feedback For Robotic Collaboration} \\
	\vspace{0.3cm}
	\Large 
	Emily Wu  \\
	Professor Stefanie Tellex \\
	Professor Jeff Huang \\
	Brown University \\
	May 2016 \\
\end{raggedleft}

\vspace*{\fill}
\section*{Abstract}
Robotic collaboration requires not just communication from the human to the robot, but also from the robot to the human. We call this robot-to-human communication \emph{social feedback}. In order to flexibly and intelligently generate social feedback, we describe a Partially Observable Markov Decision Process that incorporates the human's belief about the robot's intent. We then engineer a system that can respond in near-real time that is supplemented with a multithreaded interaction model that allows for more responsive human-robot interactions. Initial evaluation in simulation shows improvement in interaction length in a toy domain and improvement in accuracy in the full domain.
\vspace*{\fill}
\newpage
\tableofcontents
\newpage
\pagenumbering{arabic}

\maketitle
\begin{multicols}{2}

@@

\end{multicols}

@@

\bibliography{main}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{times}

% numbers option provides compact numerical references in the text. 
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

\pdfinfo{
   /Author (Homer Simpson)
   /Title  (Robots: Our new overlords)
   /CreationDate (D:20101201120000)
   /Subject (Robots)
   /Keywords (Robots;Overlords)
}

\usepackage{float}
\usepackage[margin=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{bbm}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{calc,positioning,shapes,arrows}
\newcommand{\Iota}{\mathcal{I}}

\graphicspath{{./resources/}}

\begin{document}

\title{Social Feedback For Robotic Collaboration}
\author{Author Names Omitted for Anonymous Review. Paper-ID [add your ID here]}

\maketitle

%\author{\authorblockN{Michael Shell}
%\authorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: mshell@ece.gatech.edu}
%\and
%\authorblockN{Homer Simpson}
%\authorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\authorblockN{James Kirk\\ and Montgomery Scott}
%\authorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

\begin{abstract}
Robotic collaboration requires not just communication from the human to the robot, but also from the robot to the human. We call this robot-to-human communication \emph{social feedback}. In order to flexibly and intelligently generate social feedback, we describe a Partially Observable Markov Decision Process that incorporates the human's belief about the robot's intent. We then engineer a system that can respond in near-real time that is supplemented with a multithreaded interaction model that allows for more responsive human-robot interactions. Initial evaluation in simulation shows improvement in interaction length in a toy domain and improvement in accuracy in the full domain.
\end{abstract}

@@

@@

\bibliographystyle{plainnat}
\bibliography{references}
